%%%%%%
% Vaysage.kv Resume
% Uses LaTeX and moderncv
%%%%%%

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}

\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.8]{geometry} % adjust the page margins

\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Vaysage}
\familyname{K V}
%\title{Resume}
%\address{Kaithakkal(Ho),Kandanassery(Po),Chowalloor}{Thrissur, Kerala - 680102}
\address{Kaithakkal(Ho),Kandanassery(Po)}{Thrissur, Kerala}
\mobile{+91-9916624387}
\phone{04885-237931}
\email{kvvaysage@gmail.com}
%\homepage{stultus.in}
\extrainfo{\textbf{IRC} Nick: vaysu}
%\quote {C provides a programmer with more than enough rope to hang himself.C++ provides a firing squad, blindfold and last cigarette}
%\photo[54pt]{img.jpeg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

% --------------------------------------
% CONTENT
% --------------------------------------

\begin{document}
\maketitle

\sectionblue{Education}
\cvitem{2005--2009}{\textbf{Bachelors degree} in \textit{Electronics and Communications} from Visvesvaraya Technological University with \textbf{62\%} .}
\cvitem{2003--2005}{\textbf{XII}$^{th}$ from Sri Krishna Higher Secondary School  with \textbf{85\%}.}
\cvitem{2003}{ \textbf{X}$^{th}$ from Bethany E.H.S, Kunnamkulam  with \textbf{89\%}.}

\sectionblue{Technical skills}
\cvcomputer
{\textbf{Programming Languages}}{Excellent C, C++, Java(OCJP-93\%), C\#,  XAML,  Matlab\\Shell Scripting, Oracle}
{\textbf{Operating Systems}}{GNU/Linux, Windows, Mac OSX}
\cvcomputer
{\textbf{Development Tools}}{VIM, Git, Xcode, Visual Studio \\ Expression Blend}
{\textbf{Software Packages}}{SQLite, \LaTeX, Gimp, \\Adobe Photoshop}
\cvcomputer
{\textbf{Frameworks \& Libraries}}{.NET, Silverlight \\curl, Tidy}
{}{}

% --------------------------------------
% WORK EX
% --------------------------------------

\sectionblue{Work Experience and Positions}
\cventry{Presently}{Software Engineer Trainee}{Lxi Technologies}{Pathirippala}{}{\begin{itemize} \item Learned Oracle and Java and JSP.\end{itemize}}

\cventry{July 2010 -- June 2011}{Software Engineer}{Robosoft Technologies}{Udupi}{}{\begin{itemize} \item Designed and developed a Windows phone seven application.
\item Used MVVM Design Pattern.
\item GUI was designed and developed  in XAML using Microsoft Expression Blend.
\item Model  and Controller part of program is developed using C\#. \end{itemize}}

\cventry{August 2009 -- February 2010}{Quality Assurance}{Onmobile Global}{Bangalore}{}{\begin{itemize} \item User Acceptance testing of Programs. 
\item Written shell scripts for Automating backups.
\item Written Batch programs for automating testing.\end{itemize}}

% --------------------------------------
% PROJECTS
% --------------------------------------

%\pagebreak
\sectionblue{Projects}

\cvline
{\textbf{Academic Project}}{ (Won the prize for Third Best Project)}
\cvline{Team Size:}{ 4 members.}\cvline{Languages:}{Matlab, C.}\cvline{Description:}{ Designed a maximally flat Linear phase FIR notch filter.}\cvline{}{Reduced its rejection bandwidth using Filter Sharpening Technique.}\cvline{}{Used Amplitude Change Function for Filter Sharpening.}
\cvline{}{Written a program in Matlab  and C to verify its frequency response.}


\pagebreak	
% --------------------------------------
% INTERESTS HOBBIES
% --------------------------------------

\sectionblue{Interests and Hobbies}
\cvlistitem{Reading books (Related to computers and network security) and browsing Internet.}
\cvlistitem{Downloading and reading opensource codes.}
\cvlistitem{Watching movies,Playing Cricket, Swimming etc.}

% --------------------------------------
% STRENGTHS
% --------------------------------------

\sectionblue{Strengths}
\cvlistitem{Hardworking and quick learner.}
\cvlistitem{Possess good relationship building and interpersonal skills.}
\cvlistitem{Commitment towards work.}
\cvlistitem{Quick adaptability to challenging situations.}




%-----------------------------------------------
% PERSONAL DETALILS
%-----------------------------------------------

\sectionblue{Personal Details}

\cvline{}{\textbf{Date Of Birth}}
\cvline{}{26$^{th}$ Nov, 1987}
\cvline{}{\textbf{Languages Known}}
\cvline{English}{Fluent}
\cvline{Malayalam}{Mother Tongue}
\cvline{Hindi}{Intermediate}
\cvline{Tamil}{Intermediate}
\cvline{Kannada}{Novice}
%\cvlanguage{English}{Skill level}{Comment}





%---------------- Declaration-------------------
\sectionblue{Declaration}
\cvlistitem{I hereby declare that the information furnished above is true to the best of my knowledge and belief.\\ \\ \\}

\begin{minipage}{0.5\textwidth}
\begin{flushleft}
  \large
\bfseries (Vaysage.k.v)
\end{flushleft}
\end{minipage}


%------------------------------------------


\end{document}